\input{templates/research_statement/top}

There is obvious opportunity for me to bring my hardware, software, and physics expertise to the UCI group, led by Profs. Lankford, Taffard, and Whiteson. In particular, there is a clear overlap in hardware interests as my work on gFEX, for the Level-1 Calorimeter Trigger System Phase I and Phase II upgrades, gives me experience that can support the group's work on the New Small Wheel (Phase I) and the Level-0 Muon Trigger (Phase II). My experience with trigger and data acquisition is broad, from running trigger shifts in the ATLAS Control Room, to designing and implementing a Level-1 Trigger subsystem, and developing the slow-control and monitoring infrastructure that interfaces with the existing ATLAS system. I would be excited to help participate in the testing, integration, commissioning, and installation of the instrumentation upgrades. I am also very excited about collaborating with members of the UCI group on physics analyses ranging from: hadronic resonances and searches for Dark Matter (such as Mono-Higgs), to working at the intersection of particle physics and machine learning, studying pileup mitigation techniques especially in an HL-LHC environment, and exploring new physics in the electroweak sector. The search for supersymmetry that I am involved in has set very strong limits on the mass of gluinos which raises the prospect that perhaps new physics is hiding in the electroweak sector. I would be happy to do a new kind of physics search such as Higgs or Exotics and I am confident I can quickly get up to speed. II am enthusiastic, I love to collaborate, and a post-doc position at UC Irvine is an excellent match for my current research interests.

\input{templates/research_statement/bottom_atlas}
