\input{templates/research_statement/top_v2}

There is obvious opportunity for me to bring my hardware, software, and physics expertise to the Duke HEP Group. In particular, there is a clear overlap in hardware interests as my work on gFEX, for the Level-1 Calorimeter Trigger System Phase-I/II upgrades, gives me experience that can support the group's work on the Phase-II upgrades involving the ITk strip detector. My experience with trigger and data acquisition is broad, from running trigger shifts in the ATLAS Control Room, to designing and implementing a Level-1 Trigger subsystem, and developing the slow-control and monitoring infrastructure that interfaces with the existing ATLAS system. I would be excited to help participate in the testing, integration, commissioning, and installation of the instrumentation upgrades. I am also very excited about collaborating with members of your group on physics analyses ranging from: searches for signs of new physics with top quarks, searching for signs of Dark Matter associated with Higgs production, exploring substructure techniques to enhance the current physics program, and studying pile-up mitigation techniques at the HL-LHC in the forward region of the ATLAS detector. The search for supersymmetry that I am involved in has set very strong limits on the mass of gluinos which raises the prospect that perhaps new physics is hiding in the electroweak sector. I would be happy to do a different type of search for new physics such as with Higgs or Exotics and I am confident I can quickly get up to speed. I am enthusiastic, I love to collaborate, and a post-doc position at Duke is an excellent match for my current research interests.

\input{templates/research_statement/bottom_atlas}
